A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

It is trivial to show that these two steps can be replicated for a 3-D model using HOSVD to obtain the PCA space.\\

Finally on the PCS, it is worth noting that two methods exist for obtaining PCA space\cite{Tharwat_2016} , namely, the co-variance method and the SVD method. \citet{Tharwat_2016} goes on to describe both methods in details. In this work, the authors have opted to use the SVD method to obtain the PCA space. This is because the singular vectors which make up the PCS have a strong correlation to the coordinate axis they represent. This was exploited in making the assumption that a linear relationship exist for the data in each of the PC spaces, hence the linear regression performed to reduce the data in the PCS.

>>>>

These two steps can be readily replicated for 3-D models using HOSVD to obtain the PCA space.

Finally on the PCS, it is worth noting that two methods exist for obtaining PCA space: co-variance and SVD methods (see \cite{Tharwat_2016} detailed description of both methods). In this work, the authors have opted to use the SVD method to obtain the PCA space, as singular vectors which make up the PCS have strong correlation to the coordinate axis they represent. This was exploited in making the assumption that a linear relationship exist for the data in each of the PC spaces, hence the linear regression performed to reduce the data in the PCS.
